### 2013-05-16 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
starting advanced spn preconditioning section

      purple material fuel.}}

@@

      figure is moderator and darker purple material fuel.}}

@@

%%---------------------------------------------------------------------------%%
\section{Advanced Preconditioning Strategies}
\label{subsec:spn_advanced_preconditioning}

>>>>

      purple/red material is fuel.}}

@@

      figure is moderator and darker purple/red material is fuel.}}

@@

%%---------------------------------------------------------------------------%%
\section{Advanced Preconditioning Strategies}
\label{subsec:spn_advanced_preconditioning}
For the fuel assembly criticality problem presented in the previous
section, the spectral radius was near one and in a regime in which
MCSA breakdown is observed. In this regime the number of stochastic
histories required to converge MCSA increases rapidly and the
resulting poor performance is compounded by those histories being
expensive to compute. To overcome this difficulty, advanced
preconditioning strategies are required beyond simple Jacobi methods
that can reduce the spectral radius into a region of better MCSA
performance. Several modern algebraic preconditioning strategies will
be presented here and used within the preconditioned framework given
by Eq~(\ref{eq:left_right_mcsa}). Data showing their effects on MCSA
solutions of the fuel assembly criticality problem will be presented.
